Does language control differ between younger and older adults when switching

### 2023-05-30 manuscriptINSPIRE.Rmd
Fixing bug with kableExtra installation

packagelist <- c('lme4','lmerTest','tidyverse','ggplot2','rmarkdown','bookdown','kableExtra','rstatix')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

#devtools::install_github("kupietz/kableExtra")

>>>>

packagelist <- c('lme4','lmerTest','tidyverse','ggplot2','rmarkdown','bookdown','rstatix','devtools')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

devtools::install_github("kupietz/kableExtra")
